### 2023-06-25 manuscript.tex
finished SKOS but not mapping [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/9ff6f0da1c2aa50a163efffac0fd16d3f3c6b144.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/9ff6f0da1c2aa50a163efffac0fd16d3f3c6b144/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5367047177

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/f697e5dfb9f4502a9486a03fbf56a5d69e0a6b56/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/f697e5dfb9f4502a9486a03fbf56a5d69e0a6b56}{stain/2022-fdo-paper@f697e5d}
on June 24, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/9ff6f0da1c2aa50a163efffac0fd16d3f3c6b144/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/9ff6f0da1c2aa50a163efffac0fd16d3f3c6b144}{stain/2022-fdo-paper@9ff6f0d}
on June 25, 2023.
